---
output:
  html_document: default
  pdf_document: default
---
Frederik Thurøe

Teoriorientered Metode - Digital Methods For Historians, Final Project 

```{r libraries, echo = FALSE}
#install.packages("gganimate")
#install.packages("gifski")
#install.packages("av")
#install.packages("gapminder")
#install.packages("tidyverse")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("ggplot2")
library(ggplot2)
library(tidyverse)
library(gganimate)
library(gifski)
library(av)
library(gapminder)
library(dplyr)
library(tidyr)
```


```{r, echo = FALSE}
rm(list = ls()[grep("^anim", ls())])
```


#Uploading Tidy_data_numbers_2000
```{r}
library(readr)
Tidy_data_numbers_2000 <- read_csv("Tidy_data_numbers_2000.csv", show_col_types = FALSE,
    col_types = cols(Armed_forces_personnel = col_double()))
head(Tidy_data_numbers_2000)
```

#Uploading Tidy_data_europe
```{r}
library(readr)
Tidy_data_europe <- read_csv("Tidy_data_europe.csv", show_col_types = FALSE)
head(Tidy_data_europe)
```

#Uploading Miltary_Expenditure_tidy_2020 
```{r}
library(readr)
Miltary_Expenditure_tidy_2020 <- read_csv("Miltary_Expenditure_tidy_2020.csv", show_col_types = FALSE)
head(Miltary_Expenditure_tidy_2020)
```

#Graph1: Armed forces personel vs. GDP Growth in 2000
```{r}
Graph1 <- ggplot() + 
  geom_point(aes(y = Armed_forces_personnel/100, x = GDP_growth/100, size = Size, color = Country_Name), data = Tidy_data_numbers_2000) + 
  ylab("Armed Forces Personel in % of Population") + 
  xlab("Annual GDP Growth in %") + 
  ggtitle("Armed Forces Personel vs Annual Growth in 2000") +
scale_y_continuous(label = scales::percent) + scale_x_continuous(label = scales::percent)

theme_set(theme_bw())

options(scipen = 999)
```
```{r}
Graph1
```




#Graph2: Military spending vs. GDP Growth in 2000
```{r} 
theme_set(theme_bw())

options(scipen = 999)

Graph2 <- ggplot() + 
  geom_point(aes(y = Military_expenditure/100, x = GDP_growth/100, size = Size, color = Country_Name), data = Tidy_data_numbers_2000) + 
  ylab("Military Expenditure as % of GDP") + 
  xlab("Annual GDP Growth in %") + 
  ggtitle("Military Expenditure vs. Annual Growth in 2000") +
scale_y_continuous(label = scales::percent) + scale_x_continuous(label = scales::percent)
```

```{r}
Graph2
```




#Graph3: Military spending vs. armed forces personel in 2000 
```{r} 
theme_set(theme_bw())

options(scipen = 999)

Graph3 <- ggplot() + 
  geom_point(aes(y = Military_expenditure/100, x = Armed_forces_personnel/100, size = Size, color = Country_Name), data = Tidy_data_numbers_2000) +
  ylab("Military Expenditure as % of GDP") + 
  xlab("Armed Forces Personel in % of Population") + 
  ggtitle("Military Expenditure vs. Armed Forces Personnel in 2000") +
scale_y_continuous(label = scales::percent) + scale_x_continuous(label = scales::percent)
```
```{r}
Graph3
```

#Graph4: Armed forces personel vs. GDP Growth in Europe in 2000
```{r}
theme_set(theme_bw())

options(scipen = 999)

Graph4 <- ggplot() + 
  geom_point(aes(y = Armed_forces_personnel/100, x = GDP_growth/100, size = Size, color = Region), data = Tidy_data_europe) + 
  ylab("Armed Forces Personel in % of Population") + 
  xlab("Annual GDP Growth in %") + 
  ggtitle("Annual Growth vs. Armed Forces Personel in Europe in 2000") +
scale_y_continuous(label = scales::percent) + scale_x_continuous(label = scales::percent)
```

```{r}
Graph4
```

#Graph5: Military spending vs. GDP Growth in Europe in 2000
```{r} 
theme_set(theme_bw())

options(scipen = 999)

Graph5 <- ggplot() + 
  geom_point(aes(y = Military_expenditure/100, x = GDP_growth/100, size = Size, color = Region), data = Tidy_data_europe) + 
  ylab("Military Expenditure as % of GDP") + 
  xlab("Annual GDP Growth in %") + 
  ggtitle("Military Expenditure vs. Annual Growth in Europe in 2000") +
scale_y_continuous(label = scales::percent) + scale_x_continuous(label = scales::percent)
```
```{r}
Graph5
```

#Graph6: Military spending vs. armed forces personel in Europe in 2000
```{r} 
theme_set(theme_bw())

options(scipen = 999)

Graph6 <- ggplot() + 
  geom_point(aes(y = Military_expenditure/100, x = Armed_forces_personnel/100, size = Size, color = Region), data = Tidy_data_europe) +
  ylab("Military Expenditure as % of GDP") + 
  xlab("Armed Forces Personel in % of Population") + 
  ggtitle("Military Expenditure vs.Armed Forces Personnel in Europe in 2000") +
scale_y_continuous(label = scales::percent) + scale_x_continuous(label = scales::percent)
```
```{r}
Graph6
```




Noter: scale_size(range = c(0,500))

scale_y_continuous(label = scales::percent) + scale_x_continuous(label = scales::percent)

scale_y_continuous(limits=c(0, 4)) + scale_x_continuous(limits=c(3, 11))

dt[,c(-x,-y)]





#Graph7: Military spending vs. GDP Growth in 2020
```{r} 
theme_set(theme_bw())

options(scipen = 999)

Graph7 <- ggplot() + 
  geom_point(aes(y = Military_expenditure/100, x = GDP_growth/100, size = Population, color = Region), data = Miltary_Expenditure_tidy_2020) + 
  ylab("Military Expenditure as % of GDP") + 
  xlab("Annual GDP Growth in %") + 
  ggtitle("Military Expenditure vs. Annual Growth in Europe in 2020") +
scale_y_continuous(label = scales::percent) + scale_x_continuous(label = scales::percent)
```
```{r}
Graph7
```
